### 2013-07-24 doc/asplos14/evaluation.tex
more edits. more fixes to macro usage

What is more surprising is that Grappa is able to exceed the XMT's
performance on UTS. This is a demonstration of the inflexibility of
custom hardware. Recall that the UTS benchmark searches an unbalanced
tree and spawns a data-dependent number of child tasks at each
vertex. The XMT's spawn/join semantics, whose implementation is spread
across the hardware, OS, and runtime, require a task visiting a vertex
to block until all its child tasks have completed, even though the
benchmark does not require those tasks to have completed until the end
of the tree search. Furthermore, each new task is immediately made
available to all other processors in the system, even though it is
likely that processor that spawned a task will end up executing it.

@@

Figures~\ref{fig:grappa-scaling}, \ref{fig:grappa-gups}, and
\ref{fig:grappa-uts} show scaling out to 64 nodes. Grappa scales best
on BFS and worst on IntSort, but is in general able to make use of
more nodes. Unfortunately memory limitations in our current network
library keep us from exploring scaling beyond 64 nodes; this will be
addressed in future work.

>>>>

What is more surprising is that \Grappa is able to exceed the XMT's
performance on UTS. This is a demonstration of the inflexibility of
custom hardware. Recall that the UTS benchmark searches an unbalanced
tree and spawns a data-dependent number of child tasks at each
vertex. The XMT's spawn/join semantics, whose implementation is spread
across the hardware, OS, and runtime, require a task visiting a vertex
to block until all its child tasks have completed, even though the
benchmark does not require those tasks to have completed until the end
of the tree search. Furthermore, each new task is immediately made
available to all other processors in the system, even though it is
likely that processor that spawned a task will end up executing it.

@@

Figures~\ref{fig:grappa-scaling}, \ref{fig:grappa-gups}, and
\ref{fig:grappa-uts} show scaling out to 64 nodes. \Grappa scales best
on BFS and worst on IntSort, but is in general able to make use of
more nodes. Unfortunately memory limitations in our current network
library keep us from exploring scaling beyond 64 nodes; this will be
addressed in future work.
